Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams

### 2015-01-11 Paper/paperN.tex
paper with gridsearch results

%Frame correctness: for the top 25 most probable verbs per frame $TV$ and FrameNet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
\section{Results}
These results are experimental, i.e. the parameters are guessed and therefor probably not optimal. (Since grid-search is more expensive than planned for the actual results are still in progress.) In this experiment the frames were put on $200$, $\alpha$ and $\beta$ both on $0.5$.\\
\begin{table}[h]
\centering
\begin{tabular}{|l||c|c|}
  \hline
  &dicesim&coherency\\
  \hline
  \hline
  model 0& 0.28&19\%  \\
  \hline
  model 1&0.29 &71\%  \\
  \hline
\end{tabular}
\caption{results}
\label{results}
\end{table}

\begin{table}
\begin{tabular}{|p{.3\textwidth}|p{.7\textwidth}|}
  \hline
  \textit{frame predicate} & \textit{verbs in frame}\\
  \hline
  \hline
  knowledge transfer & explain, assure, arrange, acquaint\\
  \hline
  legal accusation & prove, bother, condemn, accuse, dislike, gainsay, hypnotize\\
  \hline
  things to do with problems & solve, create, design, acquit, administer, invest, exit, recount, preview, consist\\
  \hline
  affection & love, hate\\
  \hline
  harming another &fight, shoot, invite, harm, commend, chase, seem, favour, reconstruct, pitch, request, inconvenience, redress, hitch, air, slow, disarm, strive, despoil, pique, tote, halt, bit, implicate\\
  \hline
  enjoyment & enjoy, please, bow, amount\\
  \hline
\end{tabular}
\label{exframes}
\caption{Frame examples}
\end{table}

\section{Discussion}
As table \ref{results} show, coherency  improved significantly, whereas the frame correctness did not so much. But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are assigned to a frame. It is not clear why this happens, but this are still only experimental results.  Since there are 200 frames it is obvious that the coherency is so low. Other experiments have shown that it is possible to cluster with model 0 though.

>>>>

%Frame correctness: for the top 25 most probable verbs per frame $TV$ and FrameNet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
\section{Results}
Grid search found the following parameter sets for the 2 measures. 
\begin{itemize}
  \item Best coherency with 100 frames - $\alpha$: 0.5 - $\beta$: 0.5
  \item Best accuracy with 200 frames - $\alpha$: 2 - $\beta$: 0.5
  \item Best both with 150 frames - $\alpha$: 0.1 - $\beta$: 0.5
\end{itemize}
The results on the testset are displayed in table \ref{results}. As this table shows, model 1 performs better in every case. The reslts are coherent with the above, but differences between parameter sets on model 1 are small.

 \begin{table}[h]
\centering
\begin{tabular}{|l||c|c|}
  \hline
  &accuracy&coherency\\
  \hline
  \hline
  model 0 F=100 $\alpha$=.5&0.2853 & 27.12\%  \\
  \hline
  model 1 F=100 $\alpha$=.5 $\beta$=.5& 0.3053 & 87.38\%  \\
  \hline
  model 0 F=150 $\alpha$=.1&0.2857 & 0.63\%  \\
  \hline
  model 1 F=150 $\alpha$=.1 $\beta$=.5& 0.3150 & 87.30\%  \\
  \hline
  model 0 F=200 $\alpha$=.5&0.2857 & 46.61\%  \\
  \hline
  model 1 F=200 $\alpha$=.5 $\beta$=.5&  0.3151& 87.74\%  \\
  \hline
\end{tabular}
\caption{results}
\label{results}
\end{table}

\begin{table}
\begin{tabular}{|p{.3\textwidth}|p{.7\textwidth}|}
  \hline
  \textit{frame predicate} & \textit{verbs in frame}\\
  \hline
  \hline
  knowledge transfer & explain, assure, arrange, acquaint\\
  \hline
  legal accusation & prove, bother, condemn, accuse, dislike, gainsay, hypnotize\\
  \hline
  things to do with problems & solve, create, design, acquit, administer, invest, exit, recount, preview, consist\\
  \hline
  affection & love, hate\\
  \hline
  harming another &fight, shoot, invite, harm, commend, chase, seem, favour, reconstruct, pitch, request, inconvenience, redress, hitch, air, slow, disarm, strive, despoil, pique, tote, halt, bit, implicate\\
  \hline
  enjoyment & enjoy, please, bow, amount\\
  \hline
\end{tabular}
\caption{Frame examples}
\label{exframes}
\end{table}

\section{Discussion}
As table \ref{results} shows, coherency  improved significantly, whereas the frame accuracy only marginally. Furthermore note that $\beta$ has the same value in each parameter set. In Model 1 a higher $\beta$ argues for fewer verbs per frame, with this in mind one could argue that this particular value for $\beta$ is direct resultof the number of verbs in our data. So in this case, a low $\beta$ indicates a skewed distribution of verbs over frames. This is intuitively correct, since some broader meanings can be expressed by many verbs, while others only by a few. Furthermore the results are approximately the same as \citeauthor{oconnor2013} found.
